01_LH-SIP_Data_Reduction

### 2022-06-17 01_LH-SIP_Data_Reduction.Rmd
filter assim efficiencies 0<a<1

# Simplify by only looking at the slopes
# This is what gets added to the peaks_mapped dataframes!
d2H_assim_lm_summary <- d2H_assim_lm %>% 
  ungroup() %>% 
  filter(term == "`Water dD`") %>% 
  summarize(sa = sd(estimate, na.rm = TRUE),
            a_mn = mean(estimate, na.rm = TRUE))
```

@@

# Export
```{r}
# Export as RDS
saveRDS(peaks_mapped_with_zeros_analytes_reduced,
        file = "cache/LH_SIP_data.RDS")

saveRDS(F_L_2F,
        file = "cache/heavy_label_data.RDS")

saveRDS(d2H_assim_lm_summary,
        file = "cache/d2H_assimilation.RDS")

saveRDS(LH_SIP_memcorr,
        file = "cache/LH_SIP_memcorr.RDS")

saveRDS(sample_files, 
        file = "cache/sample_files.RDS")
```

>>>>

# Simplify by only looking at the slopes
# This is what gets added to the peaks_mapped dataframes!
d2H_assim_lm_summary <- d2H_assim_lm %>% 
  ungroup() %>% 
  filter(term == "`Water dD`") %>% 
  filter(estimate >= 0,
         estimate <= 1) %>% 
  summarize(sa = sd(estimate, na.rm = TRUE),
            a_mn = mean(estimate, na.rm = TRUE))
```

@@

# Export
```{r}
# Export as RDS

# Peak data
saveRDS(peaks_mapped_with_zeros_analytes_reduced,
        file = "cache/LH_SIP_data.RDS")

# Label 2F
saveRDS(F_L_2F,
        file = "cache/heavy_label_data.RDS")

# Assimilation Efficiency Linear Model
saveRDS(d2H_assim_lm_summary,
        file = "cache/d2H_assimilation.RDS")

# Asssimilation Efficiency data
saveRDS(d2H_assim_lm,
        file = "cache/d2H_assimilation_lm.RDS")

# Memory-corrected data
saveRDS(LH_SIP_memcorr,
        file = "cache/LH_SIP_memcorr.RDS")

# Full dataset
saveRDS(sample_files, 
        file = "cache/sample_files.RDS")
```
